A parametric system for adaptive extrusion width contour parallel toolpath generation

### 2019-08-15 8_discussion.tex
lil discussion update

\subsection{Comparison of beading strategies}
\todo{Discussion of finding of Validation section}
The naive strategy and the single bead strategy are of little use to FDM printers, but they show the flexibility of our parametric system.

We can see from \cref{TEST_naive_accuracy}(top) and~\ref{over_underfill} that the naive method causes a lot of overfills and underfills: on average approximately \SI{10}{\percent} of the total target area is covered by underfill and likewise for overfill.
These defects surely influence the mechanical properties of the parts beyond a point that process parameters can reliably be correlated to mechanical properties of the part.

@@

If we look at \cref{TEST_Center_accuracy} we can see that
the centered beading strategy effectively deals with overfill and underfill and produces bead widths which are the optimal bead width in all locations, but in the center the bead widths are within a factor 2 off from the optimal bead width, which is still quite a bit.
According to \cref{over_underfill} the overfill and underfill of the over- and underfill for the centered, the evenly distributed and the inward distributed strategy are all approximately \SI{2}{\percent}, which is a considerable improvement over the naive method.

@@

The inward distributed beading strategy was introduced in order to limit the number of beads deviating from the nominal bead width and to limit the number of angled segments in transitioning regions.
The effect is difficult to see when comparing \cref{TEST_Distributed_accuracy} with~\ref{TEST_InwardDistributed_accuracy}, because there are no large solid areas in that specific shape.
Also when looking at \cref{smoothness} we cannot conclude any difference in the smoothness between the evenly distributed and the inward distributed beadign strategy.
We do not provide any statistical evidence that the inward distributed beading strategy is in fact better than the evenly distributed strategy.
However, we can say that by looking at \cref{distributed_comparison} we see that the outer toolpaths have the nominal bead width more often, which means that the inaccuracies of the adaptive bead width deposition system affect the dimensional accuracy of the outline shape less.
The errors from such inaccuracies and the errors in mechanical properties due to deviation from the nominal bead width are located near the center of the shape, which means the overal mechanical properties of the part are least affected by the discrepancy between the actual feature size and the preferred feature size when using the inward distributed beading strategy.

>>>>

\subsection{Comparison of beading strategies}
The naive strategy and the single bead strategy are of little use to FDM printers, but they show the flexibility of our parametric system.

We can see from \cref{TEST_naive_accuracy}(top) and~\ref{over_underfill} that the naive method causes a lot of overfills and underfills: on average approximately \SI{1}{\percent} of the total target area is covered by underfill and likewise for overfill.
These defects surely influence the mechanical properties of the parts beyond a point that process parameters can reliably be correlated to mechanical properties of the part.

@@

If we look at \cref{TEST_Center_accuracy} we can see that
the centered beading strategy effectively deals with overfill and underfill and produces bead widths which are the optimal bead width in all locations, but in the center the bead widths are within a factor 2 off from the optimal bead width, which is still quite a bit.
According to \cref{over_underfill} the overfill and underfill of the over- and underfill for the centered, the evenly distributed and the inward distributed strategy are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the naive method.

@@

The inward distributed beading strategy was introduced in order to limit the number of beads deviating from the nominal bead width and to limit the number of angled segments in transitioning regions.
The effect is difficult to see when comparing \cref{TEST_Distributed_accuracy} with~\ref{TEST_InwardDistributed_accuracy}, because there are no large solid areas in that specific shape.
Also when looking at \cref{smoothness} we cannot conclude any difference in the smoothness between the evenly distributed and the inward distributed beadign strategy.
We do not provide any statistical evidence that the inward distributed beading strategy is in fact better than the evenly distributed strategy.

However, we can say that by looking at \cref{distributed_comparison} we see that the outer toolpaths have the nominal bead width more often, which means that the inaccuracies of the adaptive bead width deposition system affect the dimensional accuracy of the outline shape less.
The errors from such inaccuracies and the errors in mechanical properties due to deviation from the nominal bead width are located near the center of the shape, which means the overal mechanical properties of the part are least affected by the discrepancy between the actual feature size and the preferred feature size when using the inward distributed beading strategy.
